Mathematical Aspects of the Capital Market

### 2017-08-10 phd/Chapterintroduction.tex
Revised the introduction section.

Later authors, e.g. Back \cite{back:1991} chose to model the log-price
process as a semimartingale, with increments of the Martingale
component modelled as a product process:
\begin{eqnarray*}
  Y_t &=& Y_0 + A_t + M_t \\
  M_t - M_{t-1} &=& X_t = \sigma_t Z_t
\end{eqnarray*}
where $A_t$ is a finite variation process and $M_t$ is a Martingale
and hence $Y_t$ is a semimartingale . $\sigma_t$ is non-negative and
$Z_t$ is an iid process with 0 mean and unit variance. A convenient
choice of $\sigma_t$ is
\[
\log\sigma_t = \sum_{l \in \mathbb Z} \psi_l \eta_{t-l}
\]
where $\psi_l$ is a sequence of non-negative numbers with at least one
positive element and $0 \leq \psi_l \leq 1$.

>>>>

Later authors, e.g. Back \cite{back:1991} chose to model the log-price
process as a semimartingale, with increments of the martingale
component modelled as a product process:
\begin{eqnarray*}
  Y_t &=& Y_0 + A_t + M_t \\
  M_t - M_{t-1} &=& X_t = \sigma_t Z_t
\end{eqnarray*}
where $A_t$ is a finite variation process and $M_t$ is a martingale
and hence $Y_t$ is a semimartingale. $\sigma_t$ is non-negative and
$Z_t$ is an iid process with 0 mean and unit variance. A convenient
choice of $\sigma_t$ is
\[
\log\sigma_t = \sum_{l \in \mathbb Z} \psi_l \eta_{t-l}
\]
where $-1 \leq \{\psi_l\}_{l \in \mathbb Z} \leq 1$
is a sequence of real numbers with at least one non-zero element.
